### 2019-10-21 boek.tex
update thesis
change cites
update

% figure packages
\usepackage{tikz}
\usetikzlibrary{calc,shapes,arrows,intersections,shadows}
\tikzset{>=latex}
\usepackage{graphicx}
\usepackage[indention=0.5cm,labelsep=colon,font={sf,small},labelfont={bf,sf}]{caption}
\usepackage[indention=0.5cm,font={sf,small},labelfont={bf,sf}]{subcaption}
\usepackage{float}
\usepackage{multirow}
\usepackage{import}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{tcolorbox}
\usepackage[export]{adjustbox}

@@

% table packages
\usepackage{tabularx}
\usepackage{tabulary}
\usepackage{booktabs}

@@

% references packages
\usepackage[sorting=none,refsection=chapter]{biblatex}
\bibliography{library}
\usepackage{bibentry}
\nobibliography*

@@

@@

% TIP FROM WOUTER: Per chapter, write 'update' reflecting on what came out of the paper

@@

\newpage
\graphicspath{{./ch2_dyngen/}}
\include{ch2_dyngen/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%     CH3: DYNBENCHMARK     %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 2: A comparison of single-cell trajectory inference methods} 
\chaptermark{Paper 2: A comparison of single-cell trajectory inference methods.}
\label{chap:dynbenchmark}

@@

\newpage
\graphicspath{{./ch3_dynbenchmark/}}
\include{ch3_dynbenchmark/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH4: DYNO         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 3: A toolkit for inferring and interpreting trajectories} 
\chaptermark{Paper 3: A toolkit for inferring and interpreting trajectories.} % short title
\label{chap:dyno}

@@

\newpage
\graphicspath{{./ch4_dyno/}}
\include{ch4_dyno/content}

\clearpage
\section{References}
\printbibliography[heading=none]

@@

\newpage
\graphicspath{{./ch5_scorpius/}}
\include{ch5_scorpius/content}

@@

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} \ldots \\
	\textbf{Results:} \ldots \\
	\textbf{Conclusion:} \ldots
\end{quote}

@@

\newpage
\graphicspath{{./ch6_bred/}}
\include{ch6_bred/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH7: INCGRAPH       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 6: Optimising regulatory networks} 
\chaptermark{Paper 6: Optimising regulatory networks.} % short title
\label{chap:incgraph}

@@

\newpage
\graphicspath{{./ch7_incgraph/}}
\include{ch7_incgraph/content}

@@

\newpage
\graphicspath{{./ch9_selfassessment/}}
\include{ch9_selfassessment/content}
\clearpage
\section{References}
\printbibliography[heading=none]

@@

\newpage
\graphicspath{{./ch10_guidelines/}}
\include{ch10_guidelines/content}

@@

\newpage
\graphicspath{{./ch8_discussion/}}
\include{ch8_discussion/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%        BACKMATTER         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chX_backmatter}

>>>>

% figure packages
\usepackage{tikz}
\usetikzlibrary{calc,shapes,arrows,intersections,shadows}
\tikzset{>=latex}
\usepackage{graphicx}
\usepackage[indention=0.5cm,labelsep=colon,font={sf,small},labelfont={bf,sf}]{caption}
\usepackage[indention=0.5cm,font={sf,small},labelfont={bf,sf}]{subcaption}
\usepackage{float}
\usepackage{import}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{tcolorbox}
\usepackage[export]{adjustbox} % for top alignment
\usepackage{afterpage} % for figure placement

@@

% table packages
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{tabulary}
\usepackage{booktabs}

@@

% references packages
\usepackage[sorting=none,refsection=chapter]{biblatex}
\bibliography{library}
\usepackage{bibentry}
%\nobibliography*

@@

% if switching for quick renders
\newif\ifrenderall

\renderalltrue

@@

@@

\ifrenderall
\newpage
\graphicspath{{./ch2_dyngen/}}
\include{ch2_dyngen/content}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%     CH3: DYNBENCHMARK     %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 2: A comparison of single-cell trajectory inference methods} 
\chaptermark{Paper 2: A comparison of single-cell trajectory inference methods.}
\label{chap:dynbenchmark}

@@

\ifrenderall
\newpage
\graphicspath{{./ch3_dynbenchmark/}}
\include{ch3_dynbenchmark/content}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH4: DYNO         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 3: A toolkit for inferring and interpreting trajectories} 
\chaptermark{Paper 3: A toolkit for inferring and interpreting trajectories.} % short title
\label{chap:dyno}

@@

\ifrenderall
\newpage
\graphicspath{{./ch4_dyno/}}
\include{ch4_dyno/content}

\clearpage
\section{References}
\printbibliography[heading=none]
\fi

@@

\ifrenderall
\newpage
\graphicspath{{./ch5_scorpius/}}
\include{ch5_scorpius/content}
\fi

@@

{\large \textbf{Abstract}}
\begin{quote}
	\textbf{Purpose:} Network inference methods are computational tools which use large omics datasets to predict which genes are regulated by which transcription factors.
	Since regulatory interactions are context-dependent, attempting to model regulatory dynamics in the form of a single regulatory network may have little relevance. \\
	\textbf{Results:} In this work, we introduce \texttt{bred}, the first algorithm for inferring case-wise regulatory networks. We generate . Analysing case-wise regulatory networks of 14'963 profiles from The Cancer Genome Atlas project demonstrated that regulatory interactions are often specific to particular cancer types, but can also be shared between several cancer types. \\
	\textbf{Conclusion:} Ultimately, this analysis has resulted in a list of candidate oncogenic genes and interactions per cancer type, though further analysis and validation is required to confirm their oncogenicity.
\end{quote}

@@

\ifrenderall
\newpage
\graphicspath{{./ch6_bred/}}
\include{ch6_bred/content}
\fi 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH7: INCGRAPH       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{Paper 6: Optimising regulatory networks} 
\chaptermark{Paper 6: Optimising regulatory networks.} % short title
\label{chap:incgraph}

@@

\ifrenderall
\newpage
\graphicspath{{./ch7_incgraph/}}
\include{ch7_incgraph/content}
\fi

@@

\ifrenderall
\newpage
\graphicspath{{./ch9_selfassessment/}}
\include{ch9_selfassessment/content}
\clearpage
\section{References}
\printbibliography[heading=none]
\fi

@@

\ifrenderall
\newpage
\graphicspath{{./ch10_guidelines/}}
\include{ch10_guidelines/content}
\fi

@@

\ifrenderall
\newpage
\graphicspath{{./ch8_discussion/}}
\include{ch8_discussion/content}
\fi 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%        BACKMATTER         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{chX_backmatter}
